Dynamical modeling of tidal streams

### 2014-01-01 tex/ms.tex
streams: note

>>>>

NOTES: stream feathering not included in our model, because of the
linearization of the dynamics (feathering means it's not linear over
the width of the stream. When important, can calculate actions and
angles directly (data good enough -> no need for that much
marginalization?) or, when samping mock data, use torus machinery to
calculate (X,V) better.
